A Study of Institutional Spending on Open Access Publication Fees in Germany

### 2016-06-11 article.Rmd
fixed typo
modified csl to list up to 100 authors

---
title: 'A Study of Institutional Spending on Open Access Publication Fees in Germany'
author:
- Najko Jahn, Bielefeld University Library, Bielefeld University 
- Marco Tullney, German National Library of Science and Technology (TIB), Hannover, Germany
date: "10 June 2016"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    template: peerj.sty
  html_document:
    fig_caption: yes
    force_captions: yes
    number_sections: no
    theme: readable
bibliography: literatur.bib
csl: frontiers.csl

@@

[^24]: <hhttps://github.com/OpenAPC/openapc-de/releases/tag/v2.4.3>

>>>>

---
title: 'A Study of Institutional Spending on Open Access Publication Fees in Germany'
author:
- Najko Jahn, Bielefeld University Library, Bielefeld University 
- Marco Tullney, German National Library of Science and Technology (TIB), Hannover, Germany
date: "10 June 2016"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    template: peerj.sty
  html_document:
    fig_caption: yes
    force_captions: yes
    number_sections: no
    theme: readable
bibliography: literatur.bib
csl: frontiers100.csl

@@

[^24]: <https://github.com/OpenAPC/openapc-de/releases/tag/v2.4.3>
